Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-02-25 cpm.tex
typos

\section{\name\ specification and hyper-parameters}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each month (here we always use data per month rather than quarter,  
since there is discontinuity between every 30-ish-day period),
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch more-or-less centered on the target star,
  and telemetered down once for every 30-min exposure.
(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

Let's consider a particular pixel $m$ in the focal plane in one particular month.
In that quarter, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m'n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Somewhat arbitrarily,
  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
  that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
   To rule out any direct optical cross-talk by stray
light, we require that the predictor pixels are from stars
sufficiently far away from the target star (at least 20 pixels
distance on the CCD).
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

@@

In addition to pixel set $m'\in\set{M}_m$ from other stars,  we also include
past and future of the target star --- autoregressive (AR) component as input to remove 
more of the stellar variability and thus increase the sensitivity for transits. To do this, 
we select an exclusion window of half-width $\Delta t$ including R data points, 
where $\Delta t\sim 10$ (as big 
as the window in train-and-test framework) around the point of time $t_{n}$ being 
corrected, to ensure that we do not remove the transit itself and then use S closest 
future and past time points. That is, for every pixel m in the target star , we construct S virtual time series, in which every component v is defined to be     
\begin{eqnarray}
I_{vn} = I_{mn-R-k}\ or\ I_{vn} = I_{mn+R+k},
\quad,
\end{eqnarray}
where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, we will finally add 
$2\cdot M\cdot S$ autoregressive components into the predictors,  which construct the autoregressive set $\set{V}_m$

@@

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without
signal. Based on this idea, we can construct the ``\name\ flux'' to be the relative residual
between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we 
seek. That is, a transit creates a negative residual away from the prediction.

\subsection{Hyper-parameters}
In the description of \name, we introduce 4 hyper-parameters---number of predictor 
stars Q (or number of predictor pixels P), number of autoregressive components S, and 
the two regularization strength
$\lambda_{a}$ and $\lambda_{b}$. To set these 4 hyper-parameters, in principle we 
need to run cross-validation on every single stars to optimize the performance of \name.
But optimizing in this 4-dimensional space is expensive, especially in \name\ we need 
to solve thousands of linear system with thousands of parameters. Therefore, in this 
paper we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $
\lambda_a=1e5$, $\lambda_a=1e5$) which works well in most of the stars without
highly variability. To show how this general set of hyper-parameters performs, here we 
present a typical comparison between optimized and default hyper-parameters in 
Fig~\ref{hyperparameter}. We can see that, in Fig~\ref{hyperparameter}, there is less variation in the \name\ flux from optimized hyper-parameters 
(green points in second panel) than from the default one 
(red points in the bottom panel). In addition, the optimized flux has higher signal to 
noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable and we will use  
this set of hyper-parameters throughout rest of the paper to show the general 
performance of \name.

@@

To give a view on how our method performs, \name\ is applied on several stars with 
known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
with low variation and preserving the transit signals.
In addition, \name\ and PDC are compared based on 6 quiet stars 
(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
The results illustrate that for these quiet stars our approach removes 
a major part of the variability present in the PDC light curves, while preserving the transit signals. 
To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
and estimate the Combined Differential Photometric Precision (CDPP) for \name\ and PDC. 
CDPP is an estimate of the relative precision in a time window, 
indicating the noise level seen by a transit signal with a given duration. 
The duration is typically chosen to be 3, 6, or 12 hours. 
We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
Before CDPP is estimated, the 100 most variable stars in the list are removed, 
since PDC is not designed to remove stellar variability, and we want to compare \name\ and PDC on the same footing.
Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, showing that our method (\name) outperforms PDC.

>>>>

\section{\name\ specification and hyper-parameters}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period)
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch more-or-less centered on the target star,
  and telemetered down once for every 30-min exposure.
(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

Let's consider a particular pixel $m$ in the focal plane in one particular month
(here we always use data per month rather than quarter,  
since there is discontinuity between every 30-ish-day period).
In that month, the spacecraft delivers $N\sim 1300$ measurements $I_{mn}$
  of the intensity falling in that pixel at the $N$ times $t_n$ at which exposures were taken during the month.
(For intensity measurements $I_{mn}$ here we are using pixels from the Target Pixel Files.)
We want to build a prediction for the intensity $I_{mn}$ in pixel $m$ at each time $t_n$
  using the intensities $I_{m'n}$ of other pixels $m'$.
The question is:  What other pixels to choose?
There are many possible qualitatively and quantitatively different choices here.
Somewhat arbitrarily,
  we choose all the pixels $m'$ associated with the $Q$ stars on the same CCD in the same quarter
  that are closest in magnitude
  (\Kepler\ magnitude as reported in the \Kepler\ Input Catalog)
  to the target star associated with pixel $m$.
This set of pixels%
  ---from the $Q$ stars on the same CCD---%
  is the \emph{pixel set} $\set{M}_m$ associated with pixel $m$.
   To rule out any direct optical cross-talk by starry 
light, we require that the predictor pixels are from stars
sufficiently far away from the target star (at least 20 pixels distance on the CCD).
Note that because the set $\set{M}_m$ is of pixels associated with \emph{different} stars
  than the star associated with pixel $m$, and are far from it on CCD, 
  the pixel $m$ will not be in the set $\set{M}_m$,
  and nor will any of pixel $m$'s close neighbors.
That is, there will be no (or almost no) overlap in stellar illumination of pixel $m$
  and the pixels $m'\in\set{M}_m$.

@@

In addition to pixel set $m'\in\set{M}_m$ from other stars,  
  we also include past and future of the target star --- autoregressive (AR) component as input 
  to remove more of the stellar variability and thus increase the sensitivity for transits. 
To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
  where $\Delta t\sim 10$ (as big as the window in train-and-test framework) 
  around the point of time $t_{n}$ being corrected, 
  to ensure that we do not remove the transit itself and then use S closest future and past time points. 
That is, for every pixel m in the target star , we construct S virtual time series, 
  in which every component v is defined to be     
\begin{eqnarray}
I_{vn} = I_{mn-R-k}\ or\ I_{vn} = I_{mn+R+k},
\quad,
\end{eqnarray}
where k = 0, 1, ..., S, so if there are totally M pixels in the target stars, 
  we will finally add $2\cdot M\cdot S$ autoregressive components into the predictors, 
  which constructs the autoregressive set $\set{V}_m$

@@

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without transit signal. 
Based on this idea, 
  we can construct the ``\name\ flux'' to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

\subsection{Hyper-parameters}
In the description of \name, 
  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run cross-validation on every single stars to optimize the performance of \name.
But optimizing in this 4-dimensional space is expensive, 
  especially in \name\ we need to solve thousands of linear system with thousands of parameters. 
Therefore, in this paper, 
  we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without highly variability. 
To show how this general set of hyper-parameters performs, 
  here we present a typical comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}. 
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
  than from the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout rest of the paper 
  to show the general performance of \name.

@@

To give a view on how our method performs, \name\ is applied on several stars with 
known transit signals but different variability and magnitudes as shown in Fig.~\ref{fluxes}. 
From the plots, we can see that \name\ works quite well on these stars, producing the \name\ fluxes 
with low variation and preserving the transit signals.
In addition, \name\ and PDC are compared based on 6 quiet stars 
(non-variable stars, first two rows of Fig.~\ref{fluxes}). 
The results illustrate that for these quiet stars our approach removes 
a major part of the variability present in the PDC light curves, while preserving the transit signals. 
To provide a quantitative comparison, we ran \name\ on 1000 stars from the whole Kepler input catalog 
(500 chosen randomly from the whole list, and 500 random G-type sun-like stars), 
and estimate the Combined Differential Photometric Precision (CDPP) (\todo{citation}) for \name\ and PDC. 
CDPP is an estimate of the relative precision in a time window, 
indicating the noise level seen by a transit signal with a given duration. 
The duration is typically chosen to be 3, 6, or 12 hours. 
We use the 12-hours CDPP metric, since the transit duration of an earth-like planet is roughly 10 hours. 
Before CDPP is estimated, the 100 most variable stars in the list are removed, 
since PDC is not designed to remove stellar variability, and we want to compare \name\ and PDC on the same footing.
Fig.~\ref{cdpp} presents our CDPP comparison of \name\ and PDC, showing that our method (\name) outperforms PDC.
